\plaintitle

### 2016-09-06 drafts/labor/slicing.tex
more changes

Concurrent with the body of work on the complexity of crowdsourcing
has been a thread of work exploring the decomposition of work.
In this section we'll discuss some of the approaches and the results 
the crowdsourcing community have taken from their work.
Then, as previously,
we'll discuss some of the findings that piecework research
has yielded.
Finally, we'll discuss similarities and differences between crowdwork and piecework,
and how crowdwork's limitations and potential differ from piecework's.

\subsubsubsection{\crowdworkpers}
\topic{The research on crowdwork and decomposition has generally driven toward finding new ways
to strip unnecessary context from work,
allowing tasks to be broken down into smaller parts.}
As \citeauthor{verroios2014context} frame it,
``the crowd must be able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
Researchers have thus investigated the role of
distributed, contextually independent work
in the contexts of collaborative writing of various forms,
software development,
classification, and myriad other purposes
\cite{Kittur:2009:CCI:1518701.1518928,Baecker:1993:UID:169059.169312,
      10.2307/1562247,karnin2010crowdsourcing,bragg2013crowdsourcing,
      chilton2013cascade}.

@@

\subsubsubsection{\pieceworkpers}
The beginnings of systematized task decomposition stretch back as far as the \nth{17} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to \textit{compute} astronomical phenomena
\cite{grier2013computers}.
Airy's tasks were unique at the time for several reasons:
\begin{enumerate}
  \item each task was quickly verifiable by a qualified [human] computer,
  \item tasks were discrete --- independent from one another, and
  \item knowledge of the full scope of the project --- indeed, knowledge of anything more than the problem set at hand ---
  was wholly unnecessary.
\end{enumerate}

>>>>

Concurrent with the body of work on the complexity of crowdsourcing
has been a thread of work exploring the decomposition of work.
In this section we'll discuss some of the work that
the crowdsourcing community have made toward making tasks more finite and discreet.
Then, as in the previous section,
we'll discuss some of the insights that piecework research has offered.
Finally, we'll discuss similarities and differences between crowdwork and piecework,
and how crowdwork's limitations and potential differ from piecework's.

\subsubsubsection{\crowdworkpers}
\topic{The crowdsourcing research into slicing work into smaller parts
has largely centered around removing extraneous context from the worker's view.}

While \citeauthor{Kinnaird:2012:WTM:2389176.2389219}
advocated that
greater context of the task would foster more reliably high--quality work
(especially, according to their findings, when applied to more veteran crowd workers)
% \cite{Kinnaird:2012:WTM:2389176.2389219}.
% Nevertheless,
the consensus that emerged
seems best--represented by \citeauthor{verroios2014context}'s framing of
the tension still present in the design of crowd work, that
``the crowd must be able to act with
global understanding when each contributor only has access to local views''
\cite{Kinnaird:2012:WTM:2389176.2389219,verroios2014context}.
While \citeauthor{Kinnaird:2012:WTM:2389176.2389219} showed that
it's possible to achieve higher quality work by
providing people with more information about the work they're doing,
an alternative approach to dealing with crowd workers
--- one which treats micro task workers as
``modular, protocol--defined computational services'' ---
ultimately prevailed
\cite{Kinnaird:2012:WTM:2389176.2389219,irani2015cultural}.

% Researchers have thus investigated the role of
% distributed, contextually independent work
% in the contexts of collaborative writing of various forms,
% software development,
% classification, and myriad other purposes
% \cite{Kittur:2009:CCI:1518701.1518928,Baecker:1993:UID:169059.169312,
%       10.2307/1562247,karnin2010crowdsourcing,bragg2013crowdsourcing,
%       chilton2013cascade}.

@@

\subsubsubsection{\pieceworkpers}
The beginnings of systematized task decomposition stretch back as far as the \nth{17} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to \textit{compute} astronomical phenomena
\cite{grier2013computers}.
Airy's tasks were unique at the time for several reasons:
\begin{enumerate}
  \item Each task was quickly verifiable by a qualified (human) computer;
  \item tasks were discrete --- that is, independent from one another; and
  \item knowledge of the full scope of the project
  --- indeed, knowledge of anything more than the problem set at hand ---
  was unnecessary.
\end{enumerate}
